MSCA 31006: Final Project - AQI Forecasting

### 2023-08-14 MSCA_31006_Time_Series_Final_Project - ARIMA.Rmd
ARIMA

path <- "D:/TS Final/"
pm2_5_data <- read.csv(paste0(path, "pm2.5_LA.csv"), 
                     na.strings=c("", "NA"))
ozone_data <- read.csv(paste0(path, "ozone_LA.csv"), 
                     na.strings=c("", "NA"))

@@

>>>>

path <- "/Users/sydneypeters/Desktop/"
pm2_5_data <- read.csv(paste0(path, "pm2.5_LA.csv"), 
                     na.strings=c("", "NA"))
ozone_data <- read.csv(paste0(path, "ozone_LA.csv"), 
                     na.strings=c("", "NA"))

@@

#### ARIMA model using auto.arima() - Weekly
```{r}
# Convert weekly data to a time series object
pm2_5_weekly_ts <- ts(pm2_5_weekly["19990103/20230811"], start = c(1999, 1), frequency = 52.18)

# Check stationarity, perform differencing if needed
kpss_test_result <- kpss.test(pm2_5_weekly_ts)
adf_test_result <- adf.test(pm2_5_weekly_ts)

if (kpss_test_result$p.value < 0.05 || adf_test_result$p.value < 0.05) {
  pm2_5_weekly_diff <- diff(pm2_5_weekly_ts)
} else {
  pm2_5_weekly_diff <- pm2_5_weekly_ts
}

# Fit ARIMA model using auto.arima()
arima_model_weekly <- auto.arima(pm2_5_weekly_diff)

# Forecast using ARIMA model
forecast_arima_weekly <- forecast(arima_model_weekly, h = h)
plot(forecast_arima_weekly)
```
#### ARIMA model using auto.arima() - Monthly
```{r}
# Convert monthly data to a time series object
pm2_5_monthly_ts <- ts(pm2_5_monthly["19990131/20230811"], start = c(1999, 1), frequency = 12)

# Check stationarity, perform differencing if needed
kpss_test_result <- kpss.test(pm2_5_monthly_ts)
adf_test_result <- adf.test(pm2_5_monthly_ts)

if (kpss_test_result$p.value < 0.05 || adf_test_result$p.value < 0.05) {
  pm2_5_monthly_diff <- diff(pm2_5_monthly_ts)
} else {
  pm2_5_monthly_diff <- pm2_5_monthly_ts
}

# Fit ARIMA model using auto.arima()
arima_model_monthly <- auto.arima(pm2_5_monthly_diff)

# Forecast using ARIMA model
forecast_arima_monthly <- forecast(arima_model_monthly, h = h)
plot(forecast_arima_monthly)
```
